Unit tests

### 2018-04-03 Tests.Rmd
changes to bivariate model selection to exclude negatively correlated pairs

Now apply the function:
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(d,mtime("OurBiCopSelect.R"))}
families<-c(1,3,4,5,13)
BivMS_res_test<-OurBiCopSelect(d[,1],d[,2],families=families,gofnormal=TRUE,status=TRUE)
```

@@

@@

<!--Shya to add headers for other things that need to be tested, and let's discuss before you add the tests themselves-->

>>>>

Now apply the function:
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(d,mtime("OurBiCopSelect.R"))}
families<-c(1,3,4,5,13)
BivMS_res_test<-OurBiCopSelect(d[,1],d[,2],families=families,gofnormal=F,status=TRUE)
```

@@

Tau value should be positive:
```{r echo=T}
BivMS_res_test$TauVal
```

@@

Now test with negatively correlated data, which happens ocassionally:

Data are simulated from a normal copula with parameter $-0.2$:
```{r get_neg_dat, echo=T}
set.seed(101)
cop<-normalCopula(-0.2,2,dispstr="un")
d<-rCopula(1000,cop)
v<-getcopula(d=d,rankon=F,ploton=T) #with real data, rankon should be T
```

Make sure the correlatation is negative for these data:
```{r test_neg_dat, echo=T}
cor(v[,1],v[,2],method="kendall")
```

Call `OurBiCopSelect` - all is should do is test independence, reject independence,
get tau and find it negative and then stop:
```{r test_OurBiCopSelect_neg, echo=T, cache=T, cache.extra=list(v,mtime("OurBiCopSelect.R"))}
res<-OurBiCopSelect(v[,1],v[,2],families=c(1,3,9),level=0.05,AICBIC="AIC",
                         numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                         gofnormal=F,status=TRUE)
res
```
